### 2020-07-20 steadystate.tex
change to plasma color map
final comments and edits from katy

\begin{figure}[htbp!]
    \centering
    \begin{subfigure}[t]{.365\textwidth}
        \centering
        \includegraphics[width=\textwidth]{flow-temp}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{.625\textwidth}
        \centering
        \includegraphics[width=\textwidth]{flow-temp-fiorina}
    \end{subfigure}
    \caption{Temperature and velocity fields in the core from Moltres
    (left), Polimi (center), and TUDelft (right) models. The colors represent
    temperature according to the respective color bars and the arrows
    represent velocity fields.}
    \label{fig:flow-temp}
\end{figure}

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.6\textwidth]{flow}
    \caption{Fuel salt flow streamlines and velocity magnitude in the core.
    The colors represent velocity magnitude according to the color bar on the
    right.}
    \label{fig:flow}
\end{figure}

@@

\begin{figure}[b!]
    \centering
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{ss-g1}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{ss-g2}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{ss-g3}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{ss-g4}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{ss-g5}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{ss-g6}
    \end{subfigure}
    \caption{Neutron flux distributions in the core for neutron energy groups
    1 to 6. The y and x axes represent height and radius (in cm) of the core
    relative to the entire reactor geometry.}
    \label{fig:neutronflux}
\end{figure}

@@

\begin{figure}[t!]
    \centering
    \begin{subfigure}[t]{.243\textwidth}
        \centering
        \includegraphics[width=\textwidth]{ss-pre1}
    \end{subfigure}
    \begin{subfigure}[t]{.243\textwidth}
        \centering
        \includegraphics[width=\textwidth]{ss-pre2}
    \end{subfigure}
    \begin{subfigure}[t]{.243\textwidth}
        \centering
        \includegraphics[width=\textwidth]{ss-pre3}
    \end{subfigure}
    \begin{subfigure}[t]{.243\textwidth}
        \centering
        \includegraphics[width=\textwidth]{ss-pre4}
    \end{subfigure}
    \begin{subfigure}[t]{.243\textwidth}
        \centering
        \includegraphics[width=\textwidth]{ss-pre5}
    \end{subfigure}
    \begin{subfigure}[t]{.243\textwidth}
        \centering
        \includegraphics[width=\textwidth]{ss-pre6}
    \end{subfigure}
    \begin{subfigure}[t]{.243\textwidth}
        \centering
        \includegraphics[width=\textwidth]{ss-pre7}
    \end{subfigure}
    \begin{subfigure}[t]{.243\textwidth}
        \centering
        \includegraphics[width=\textwidth]{ss-pre8}
    \end{subfigure}
    \caption{\gls{DNP} distributions in the core for \gls{DNP} groups
    1 to 8 (from left to right, top to bottom). Refer to Figure \ref{fig:neutronflux} for the height and radius
    scales on the y and x axes, respectively. Note the different scales for
    each distribution.}
    \label{fig:dnp}
\end{figure}

@@

\begin{figure}[b!]
    \centering
    \begin{subfigure}[t]{.30\textwidth}
        \centering
        \vspace{.9cm}
        \includegraphics[width=\textwidth]{ss-pre}
    \end{subfigure}
    \begin{subfigure}[t]{.69\textwidth}
        \centering
        \vspace{0pt}
        \includegraphics[width=\textwidth]{fiorina-pre}
    \end{subfigure}
    \caption{Total delayed neutron source distribution in the core from
    Moltres (left), Polimi (center), and TUDelft (right) models.}
    \label{fig:pre}
\end{figure}

@@

Figure \ref{fig:decayheat} shows the decay heat source distribution in the
core for groups 1 to 3. The decay constants are $\lambda_j = 0.197$ s$^{-1},
0.0168$ s$^{-1}, 0.000358$ s$^{-1}$ for decay heat groups $j=$ 1, 2, and 3,
respectively.
Similar to the delayed neutron precursor distributions, the shorter-lived
decay heat precursors show greater build-up in the recirculation zones
compared with the longer-lived decay heat precursors that are more evenly
distributed throughout the core.

\begin{figure}[htbp!]
    \centering
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{heat1}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{heat2}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{heat3}
    \end{subfigure}
    \caption{Decay heat source distribution in the core for decay heat groups
    1 to 3 (from left to right). Refer to Figure \ref{fig:decayheattemp} for
    the height and radius scales on the y and x axes, respectively. Note the
    different scales for each distribution.}
    \label{fig:decayheat}
\end{figure}

Figure \ref{fig:decayheattemp} shows the
difference in core temperatures at steady state with decay heat modeling
relative to the core temperatures without decay heat in Figure
\ref{fig:flow-temp}. This figure uses a different color map to clearly
distinguish between positive and negative temperature differences in the core.
The hotspots in the recirculation zones are approximately
2 to 4 K cooler, while the cooled salt flowing in from the inlet is
approximately 2 K hotter. These regions correspond to the hottest and coldest
areas in the core and the results agree with the expectation that the extreme
temperatures would be affected the most by the introduction of decay heat
precursors. The difference between the outlet and inlet temperatures falls
from 101.1 K to 98.9 K as some of the decay heat precursors deposit heat in
the outer loop region. The figure also shows some unphysical oscillations in
the temperature near the outlet because the mesh near the boundary is too
coarse. Users can avoid these oscillations near the outlet by using a mesh
that is progressively finer towards the boundary. The
present author could not resolve this issue due to time constraints.

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.6\textwidth]{decay-heat-temp}
    \caption{Difference in core temperatures at steady state with decay heat
    relative to the result without decay heat (Figure \ref{fig:flow-temp}).}
    \label{fig:decayheattemp}
\end{figure}

>>>>

\begin{figure}[htbp!]
    \centering
    \begin{subfigure}[t]{.35\textwidth}
        \centering
        \includegraphics[width=\textwidth]{flow-temp-plasma}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{.625\textwidth}
        \centering
        \includegraphics[width=\textwidth]{flow-temp-fiorina}
    \end{subfigure}
    \caption{Temperature and velocity fields in the core from Moltres
    (left), Polimi (center), and TUDelft (right) models. The colors represent
    temperature according to the respective color bars and the arrows
    represent velocity fields.}
    \label{fig:flow-temp}
\end{figure}

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.58\textwidth]{flow-plasma}
    \caption{Fuel salt flow streamlines and velocity magnitude in the core.
    The colors represent velocity magnitude according to the color bar on the
    right.}
    \label{fig:flow}
\end{figure}

@@

\begin{figure}[b!]
    \centering
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{g1}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{g2}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{g3}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{g4}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{g5}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{g6}
    \end{subfigure}
    \caption{Neutron flux distributions in the core for neutron energy groups
    1 to 6. The y and x axes represent height and radius (in cm) of the core
    relative to the entire reactor geometry.}
    \label{fig:neutronflux}
\end{figure}

@@

\begin{figure}[t!]
    \centering
    \begin{subfigure}[t]{.243\textwidth}
        \centering
        \includegraphics[width=\textwidth]{pre1}
    \end{subfigure}
    \begin{subfigure}[t]{.243\textwidth}
        \centering
        \includegraphics[width=\textwidth]{pre2}
    \end{subfigure}
    \begin{subfigure}[t]{.243\textwidth}
        \centering
        \includegraphics[width=\textwidth]{pre3}
    \end{subfigure}
    \begin{subfigure}[t]{.243\textwidth}
        \centering
        \includegraphics[width=\textwidth]{pre4}
    \end{subfigure}
    \begin{subfigure}[t]{.243\textwidth}
        \centering
        \includegraphics[width=\textwidth]{pre5}
    \end{subfigure}
    \begin{subfigure}[t]{.243\textwidth}
        \centering
        \includegraphics[width=\textwidth]{pre6}
    \end{subfigure}
    \begin{subfigure}[t]{.243\textwidth}
        \centering
        \includegraphics[width=\textwidth]{pre7}
    \end{subfigure}
    \begin{subfigure}[t]{.243\textwidth}
        \centering
        \includegraphics[width=\textwidth]{pre8}
    \end{subfigure}
    \caption{\gls{DNP} distributions in the core for \gls{DNP} groups
    1 to 8 (from left to right, top to bottom). Refer to Figure \ref{fig:neutronflux} for the height and radius
    scales on the y and x axes, respectively. Note the different scales for
    each distribution.}
    \label{fig:dnp}
\end{figure}

@@

\begin{figure}[b!]
    \centering
    \begin{subfigure}[t]{.30\textwidth}
        \centering
        \vspace{.9cm}
        \includegraphics[width=\textwidth]{pre}
    \end{subfigure}
    \begin{subfigure}[t]{.69\textwidth}
        \centering
        \vspace{0pt}
        \includegraphics[width=\textwidth]{fiorina-pre}
    \end{subfigure}
    \caption{Total delayed neutron source distribution in the core from
    Moltres (left), Polimi (center), and TUDelft (right) models.}
    \label{fig:pre}
\end{figure}

@@

\begin{figure}[htbp!]
    \centering
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{heat1-plasma}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{heat2-plasma}
    \end{subfigure}
    \begin{subfigure}[t]{.325\textwidth}
        \centering
        \includegraphics[width=\textwidth]{heat3-plasma}
    \end{subfigure}
    \caption{Decay heat source distribution in the core for decay heat groups
    1 to 3 (from left to right). Refer to Figure \ref{fig:decayheattemp} for
    the height and radius scales on the y and x axes, respectively. Note the
    different scales for each distribution.}
    \label{fig:decayheat}
\end{figure}

Figure \ref{fig:decayheat} shows the decay heat source distribution in the
core for groups 1 to 3. Readers may refer to Table
\ref{table:decayheat} for the associated decay time constants.
Similar to the delayed neutron precursor distributions, the shorter-lived
decay heat precursors show greater build-up in the recirculation zones
compared with the longer-lived decay heat precursors that are more evenly
distributed throughout the core.

Figure \ref{fig:decayheattemp} shows the
difference in core temperatures at steady state with decay heat modeling
relative to the core temperatures without decay heat in Figure
\ref{fig:flow-temp}. This figure uses a different color map to clearly
distinguish between positive and negative temperature differences in the core.
The hotspots in the recirculation zones are approximately
2 to 4 K cooler, while the cooled salt flowing in from the inlet is
approximately 2 K hotter. These regions correspond to the hottest and coldest
areas in the core and the results agree with the expectation that the extreme
temperatures would be affected the most by the introduction of decay heat
precursors. The difference between the outlet and inlet temperatures falls
from 101.1 K to 98.9 K as some of the decay heat precursors deposit heat in
the outer loop region. The figure also shows some nonphysical oscillations in
the temperature near the outlet because the mesh near the boundary is too
coarse for the given outlet velocities. Users can avoid these oscillations
near the outlet by using a mesh
that is progressively finer towards the boundary. The
present author could not resolve this issue due to time constraints.

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.55\textwidth]{decay-heat-temp}
    \caption{Difference in core temperatures at steady state with decay heat
    relative to the result without decay heat (Figure \ref{fig:flow-temp}).}
    \label{fig:decayheattemp}
\end{figure}

### 2020-07-20 transient.tex
final comments and edits from katy

This chapter discusses Moltres transient multiphysics simulations of the
\gls{MSFR} in four accident scenarios. These scenarios, adapted from the
\gls{MSFR} transient analyses with the Polimi and TUDelft models
\cite{fiorina_modelling_2014}, include unprotected reactivity
insertion, loss of heat sink, loss of flow, and pump overspeed accidents. The
term ``unprotected'' signify accident scenarios without treactor SCRAM. As
such, these simulations provide an insight on the
\gls{MSFR}'s passive safety capabilities in the absence
of active safety systems. This work used the steady-state configuration
presented in the previous chapter as the initial conditions for the transient
simulations discussed in this chapter. Specifically, all steady-state spatial
values for neutron flux, delayed neutron precursor concentration, temperature,
velocity, and pressure were imported as the initial state of the transient
scenarios.

@@

Figure \ref{fig:polimidecaytemp} shows the loop-averaged temperature
increase in the Moltres and Polimi models \cite{fiorina_modelling_2014}. The
TUDelft model does not have a decay heat modeling capability. The Moltres
model predicts the same increasing trend in the temperature. The loop-averaged
temperature rises significantly at the start of the transient and continues to
rise at a decreasing rate. The loop-averaged temperature increase in the
Moltres model at $t=120$ s is approximately 17 K lower than that in the Polimi
model. It is difficult to ascertain the exact cause for this difference
without the power profile from the Polimi model with decay heat to compare
with. However, if the decay power output are similar, the stronger negative
temperature reactivity coefficient would cause the prompt power output in the
Moltres model to fall faster than the Polimi model. Consequently, the
loop-averaged temperature would be lower as shown in the figure. Overall, the
results for the loss of heat sink transient agree with the Polimi and TUDelft
model results in both cases, with and without decay heat modeling.

@@

This work followed Fiorina et al.'s implementation
\cite{fiorina_modelling_2014} by
ramping up the inlet velocity, $u$, by 50\% from the nominal value, $u_0$,
according to the following formula:
%
\begin{align}
    u(t) &= u_0 [1 + 0.5 (1 - e^{-t / \tau})] \label{eq:overspeed}
    \intertext{where}
    \tau &= 5 \text{ s.} \nonumber
\end{align}
%
For this transient, this work assumed that $\mu_t$ was directly proportional
to $v$ because the buoyancy effects are assumed to be negligible with forced
flow and the recirculation zones 
persist throughout the entire duration.

Setting the exact dependence between the heat transfer coefficient $h$ and
$\dot{V}$ was problematic because
the pointwise heat exchanger implementation in Moltres performs differently
compared with the heat exchangers of finite volume in the Polimi and TUDelft
models \cite{fiorina_modelling_2014}. In a heat exchanger of finite volume,
most of the cooling occurs in the first half of the heat exchanger where the
temperature differential between the primary and intermediate loops is the
largest. In the Polimi and TUDelft models, the overall $h$ is a
harmonic mean of the $h_i$ on each side of the heat exchanger, given as:
%
\begin{align}
    h &= \frac{2}{\frac{1}{h_1} + \frac{1}{h_2}}, \\
    \intertext{where}
    h &= \text{overall heat transfer coefficient
    [W$\cdot$K$^{-1}$],} \nonumber \\
    h_1 &= \text{heat transfer coefficient on the primary loop side
    [W$\cdot$K$^{-1}$],} \nonumber \\
    h_2 &= \text{heat transfer coefficient on the intermediate loop side
    [W$\cdot$K$^{-1}$].} \nonumber
\end{align}
%
In addition to this, Fiorina et al. applied the Dittus-Boelter correlation
\cite{dittus_heat_1930} for the relationship between $h_1$ and
$\dot{V}$. The Dittus-Boelter correlation for fluids being cooled is:
%
\begin{align}
    Nu &= 0.023 Re^{0.8} Pr^{0.3}, \label{eq:db} \\
    \intertext{where}
    Nu &= \text{Nusselt number,} \nonumber \\
    &\text{\ \ \ \ \ the ratio of convective to conductive heat
    transfer at a boundary in a fluid,} \nonumber \\
    Re &= \text{Reynolds number,} \nonumber \\
    &\text{\ \ \ \ \ the ratio of inertial forces to viscous
    forces within a fluid,} \nonumber \\
    Pr &= \text{Prandtl number,} \nonumber \\
    &\text{\ \ \ \ \ the ratio of momentum diffusivity to thermal
    diffusivity.} \nonumber
\end{align}
%
The only direct relation to $\dot{V}$ in the Dittus-Boelter correlation is
through the Reynolds number, $Re$, which is directly proportional to
flow velocity $v$. This gives the following relation between $h$ and $v$:
%
\begin{align}
    h &\propto v^{0.8} \label{eq:hv} \\
    h &= \text{heat transfer coefficient [W$\cdot$K$^{-1}$],} \nonumber \\
    v &= \text{flow velocity [m$\cdot$s$^{-1}$].} \nonumber
\end{align}
%
However, this relation provided very different results in the unprotected pump
overspeed and loss of flow transients compared with the Polimi and TUDelft
models. This approach underpredicted the equilibrium power output in the
unprotected pump overspeed transient and overpredicted the same parameter in
the unprotected loss of flow transient. Upon further investigation, I
found that raising the power of $v$ from 0.8 to 1.1 brought the
average core temperatures closer to the results from the other models in both
transients. Therefore, this work adopted the raised power in this thesis.

@@

A loss of forced flow transient can occur in the event of a station blackout
without reactor SCRAM; the pumps would cease operating due to the loss of AC
electrical
power. Natural circulation resulting from temperature-dependent density
changes becomes the dominant driving force for salt flow in the primary loop.
Fiorina et al. \cite{fiorina_modelling_2014} applied the Boussinesq
approximation for buoyancy-driven flow in the Polimi and TUDelft models, but
this approach was not possible in Moltres because the primary loop is
partitioned into two separate geometries and used Dirichlet boundary
conditions at the inlet to drive flow. The Polimi and TUDelft
models featured complete exponential coast-downs of the pumps with a time
constant of 5 s. The final flow rate $\dot{V}_f$ from natural circulation
was approximately 18 times smaller than the initial $\dot{V}_0$. Figure
\ref{fig:flowrate} shows that the actual $\dot{V}$ decreased with a time
constant of 8 s. Thus, for the \gls{MSFR} model in Moltres, this work imposed
a similar exponential decay term with a time constant of 8 s on the inflow
Dirichlet boundary condition:
%
\begin{align}
    \dot{V} &= \dot{V}_f + (\dot{V}_0-\dot{V}_f) e^{-t/8},
    \label{eq:flowrate} \\
    \intertext{where}
    \dot{V}_f &= \text{final volumetric flow rate} = 0.25862
    \text{ m$^3\cdot$s$^{-1}$,} \nonumber \\
    \dot{V}_0 &= \text{initial volumetric flow rate} = 4.5
    \text{ m$^3\cdot$s$^{-1}$.} \nonumber
\end{align}

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.7\textwidth]{lof-flow-rate}
    \caption{The change in flow rate in the Polimi and TUDelft models and the
    imposed flow rate in Moltres.}
    \label{fig:flowrate}
\end{figure}
%
The reduced $\dot{V}$ also decreases the heat transfer rate between the
primary and intermediate loop through the heat exchanger as the heat transfer
coefficient $h$ is dependent on the $\dot{V}$. For this loss of flow
transient, Fiorina et al. \cite{fiorina_modelling_2014} intended to focus
on the primary loop and assumed that only the pumps in the primary loop
failed.

An issue arose pertaining to the turbulent viscosity $\mu_t$ as a function of
$v$. When using a simple approximation of $\mu_t$ being directly proportional
to $v$, the results from Moltres differed significantly compared with the
Polimi and TUDelft models. The difference is due to buoyancy-driven flow
contributing to turbulence; the turbulent energy $k$ equation in COMSOL's
$k$-$\epsilon$ model has an explicit source term from buoyancy effects
\cite{comsol_ab_comsol_2018}. Another point to note is the
Reynolds number remains constant if $\mu$ and $v$ decrease in tandem. This
preserves the existence of the recirculation zone in the core and it is at
odds with the results from the Polimi and TUDelft models, which show that the
recirculation zones disappear during the loss of flow transient. The current
work circumvented this issue by letting fixed fractions of the initial
$\mu_{t,0}$ be conserved regardless of the final flow velocity, according to
the following equation:
%
\begin{align}
    \mu_t &= \mu_c + (\mu_{t,0} - \mu_c) e^{-t/8} \label{lofmu} \\
    \intertext{where}
    \mu_c &= \text{ conserved fraction of $\mu_{t,0}$ [Pa$\cdot$s].} \nonumber
\end{align}
%
This measure allowed for laminar flow to develop in the core and yielded
results showing better qualitative agreement with those from the Polimi and
TUDelft models. The subsequent paragraphs discuss these results.

@@

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.37\textwidth]{lof-flow-temp}
    \includegraphics[width=.62\textwidth]{fiorina-lof}
    \caption{Temperature and velocity fields in the core at $t=300$ s during
    a loss of flow transient in the Moltres ($\mu_c = \frac{1}{2} \mu_{t,0}$),
    Polimi, and TUDelft models.}
    \label{fig:lofflowtemp}
\end{figure}

>>>>

This chapter discusses Moltres transient multiphysics simulations of the
\gls{MSFR} in four accident scenarios. These scenarios, adapted from the
\gls{MSFR} transient analyses with the Polimi and TUDelft models
\cite{fiorina_modelling_2014}, include unprotected reactivity
insertion, loss of heat sink, loss of flow, and pump overspeed accidents. The
term ``unprotected'' signifies accident scenarios without treactor SCRAM. As
such, these simulations provide an insight on the
\gls{MSFR}'s passive safety capabilities in the absence
of active safety systems. This work used the steady-state configuration
presented in the previous chapter as the initial conditions for the transient
simulations discussed in this chapter. Specifically, all steady-state spatial
values for neutron flux, delayed neutron precursor concentration, temperature,
velocity, and pressure were imported as the initial state of the transient
scenarios.

@@

Figure \ref{fig:polimidecaytemp} shows the loop-averaged temperature
increase in the Moltres and Polimi models \cite{fiorina_modelling_2014}. The
TUDelft model does not have a decay heat modeling capability. The Moltres
model predicts the same increasing trend in the temperature. The loop-averaged
temperature rises significantly at the start of the transient and continues to
rise at a decreasing rate. The loop-averaged temperature increase in the
Moltres model at $t=120$ s is approximately 17 K lower than that in the Polimi
model. It is difficult to ascertain the exact cause for this difference
without the power profile from the Polimi model with decay heat to compare
with. However, if the decay power output were similar, the stronger negative
temperature reactivity coefficient would cause the prompt power output in the
Moltres model to fall faster than the Polimi model. Consequently, the
loop-averaged temperature would be lower as shown in the figure. Overall, the
results for the loss of heat sink transient agree with the Polimi and TUDelft
model results in both cases, with and without decay heat modeling.

@@

This work followed the Polimi and TUDelft models
\cite{fiorina_modelling_2014} by
ramping up the inlet velocity, $u$, by 50\% from the nominal value, $u_0$,
according to the following formula:
%
\begin{align}
    u(t) &= u_0 [1 + 0.5 (1 - e^{-t / \tau})] \label{eq:overspeed}
    \intertext{where}
    \tau &= 5 \text{ s.} \nonumber
\end{align}
%
For this transient, this work assumed that $\mu_t$ was directly proportional
to $v$ because the buoyancy effects are assumed to be negligible with forced
flow and the recirculation zones 
persist throughout the entire duration.

Setting the exact dependence between the heat transfer coefficient $h$ and
$\dot{V}$ was problematic because
the pointwise heat exchanger implementation in Moltres performs differently
compared with the heat exchangers of finite volume in the Polimi and TUDelft
models \cite{fiorina_modelling_2014}. In a heat exchanger of finite volume,
most of the cooling occurs in the first half of the heat exchanger where the
temperature differential between the primary and intermediate loops is the
largest. In the Polimi and TUDelft models, the overall $h$ is a
harmonic mean of the $h_i$ on each side of the heat exchanger, given as:
%
\begin{align}
    h &= \frac{2}{\frac{1}{h_1} + \frac{1}{h_2}}, \\
    \intertext{where}
    h &= \text{overall heat transfer coefficient
    [W$\cdot$K$^{-1}$],} \nonumber \\
    h_1 &= \text{heat transfer coefficient on the primary loop side
    [W$\cdot$K$^{-1}$],} \nonumber \\
    h_2 &= \text{heat transfer coefficient on the intermediate loop side
    [W$\cdot$K$^{-1}$].} \nonumber
\end{align}
%
In addition to this, the Polimi and TUDelft models used the Dittus-Boelter
correlation \cite{dittus_heat_1930} for the relationship between $h_1$ and
$\dot{V}$. The Dittus-Boelter correlation for fluids being cooled is:
%
\begin{align}
    Nu &= 0.023 Re^{0.8} Pr^{0.3}, \label{eq:db} \\
    \intertext{where}
    Nu &= \text{Nusselt number} =
    \frac{\text{convective heat transfer}}{\text{conductive heat transfer}}
    = \frac{hL}{k}, \nonumber \\
    Re &= \text{Reynolds number} =
    \frac{\text{inertial forces}}{\text{viscous forces}} =
    \frac{\rho u L}{\mu}, \nonumber \\
    Pr &= \text{Prandtl number} =
    \frac{\text{momentum diffusivity}}{\text{thermal diffusivity}} =
    \frac{c_p \mu}{k}. \nonumber
\end{align}
%
The only direct relation to $\dot{V}$ in the Dittus-Boelter correlation is
through the Reynolds number, $Re$, which is directly proportional to
flow velocity $v$. This gives the following relation between $h$ and $v$:
%
\begin{align}
    h &\propto v^{0.8} \label{eq:hv} \\
    h &= \text{heat transfer coefficient [W$\cdot$K$^{-1}$],} \nonumber \\
    v &= \text{flow velocity [m$\cdot$s$^{-1}$].} \nonumber
\end{align}
%
However, this relation provided very different results in the unprotected pump
overspeed and loss of flow transients compared with the Polimi and TUDelft
models. This approach underpredicted the equilibrium power output in the
unprotected pump overspeed transient and overpredicted the same parameter in
the unprotected loss of flow transient. Upon further investigation, I
found that raising the power of $v$ from 0.8 to 1.1 brought the
average core temperatures closer to the results from the other models in both
transients. Therefore, this work adopted the raised power in this thesis.

@@

A loss of forced flow transient can occur in the event of a station blackout
without reactor SCRAM; the pumps would cease operating due to the loss of AC
electrical
power. Natural circulation resulting from temperature-dependent density
changes becomes the dominant driving force for salt flow in the primary loop.
Fiorina et al. \cite{fiorina_modelling_2014} applied the Boussinesq
approximation for buoyancy-driven flow in the Polimi and TUDelft models, but
this approach was not possible in Moltres because the primary loop is
partitioned into two separate geometries and used Dirichlet boundary
conditions at the inlet to drive flow. The Polimi and TUDelft
models featured complete exponential coast-downs of the pumps with a time
constant of 5 s. The final flow rate $\dot{V}_f$ from natural circulation
was approximately 18 times smaller than the initial $\dot{V}_0$. Figure
\ref{fig:flowrate} shows that the actual $\dot{V}$ decreased with a time
constant of 8 s. Thus, for the \gls{MSFR} model in Moltres, this work imposed
a similar exponential decay term with a time constant of 8 s on the inflow
Dirichlet boundary condition:
%
\begin{align}
    \dot{V} &= \dot{V}_f + (\dot{V}_0-\dot{V}_f) e^{-t/8},
    \label{eq:flowrate} \\
    \intertext{where}
    \dot{V}_f &= \text{final volumetric flow rate} = 0.25862
    \text{ m$^3\cdot$s$^{-1}$,} \nonumber \\
    \dot{V}_0 &= \text{initial volumetric flow rate} = 4.5
    \text{ m$^3\cdot$s$^{-1}$.} \nonumber
\end{align}
%
\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.6\textwidth]{lof-flow-rate}
    \caption{The change in flow rate in the Polimi and TUDelft models and the
    imposed flow rate in Moltres.}
    \label{fig:flowrate}
\end{figure}
%
The reduced $\dot{V}$ also decreases the heat transfer rate between the
primary and intermediate loop through the heat exchanger as the heat transfer
coefficient $h$ is dependent on the $\dot{V}$. For this loss of flow
transient, Fiorina et al. \cite{fiorina_modelling_2014} intended to focus
on the primary loop and assumed that only the pumps in the primary loop
failed.

An issue arose pertaining to the turbulent viscosity $\mu_t$ as a function of
$v$. When using this simple approximation, in which $\mu_t$ being directly
proportional
to $v$, the results from Moltres differed significantly compared with the
Polimi and TUDelft models. The difference is due to buoyancy-driven flow
contributing to turbulence; the turbulent energy $k$ equation in COMSOL's
$k$-$\epsilon$ model has an explicit source term from buoyancy effects
\cite{comsol_ab_comsol_2018}. Another point to note is the
Reynolds number remains constant if $\mu$ and $v$ decrease in tandem. This
preserves the existence of the recirculation zone in the core and it is at
odds with the results from the Polimi and TUDelft models, which show that the
recirculation zones disappear during the loss of flow transient. The current
work circumvented this issue by letting fixed fractions of the initial
$\mu_{t,0}$ be conserved regardless of the final flow velocity, according to
the following equation:
%
\begin{align}
    \mu_t &= \mu_c + (\mu_{t,0} - \mu_c) e^{-t/8} \label{lofmu} \\
    \intertext{where}
    \mu_c &= \text{ conserved fraction of $\mu_{t,0}$ [Pa$\cdot$s].} \nonumber
\end{align}
%
This measure allowed for laminar flow to develop in the core and yielded
results showing better qualitative agreement with those from the Polimi and
TUDelft models. The subsequent paragraphs discuss these results.

@@

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=.37\textwidth]{lof-plasma}
    \includegraphics[width=.62\textwidth]{fiorina-lof}
    \caption{Temperature and velocity fields in the core at $t=300$ s during
    a loss of flow transient in the Moltres ($\mu_c = \frac{1}{2} \mu_{t,0}$),
    Polimi, and TUDelft models.}
    \label{fig:lofflowtemp}
\end{figure}
